Consistent ecosystem functional response across precipitation extremes in a sagebrush steppe

### 2017-08-21 manuscript/usses_water_ms.Rmd
trivia

Cumulative March-June soil moisture had a weak positive effect on ANPP (Table 1; Fig. 3), but the effect is associated with high uncertainty, with credible intervals that overlap zero (Table 1).
Ecosystem functional response was similar among treatments (Table 1; Fig. 3), but there is evidence that the slope for the irrigation treatment is less than the slope for the control treatment.
This evidence comes from interpreting the posterior distribution of the slope offset for the irrigation treatment, from which we calculate a 98% probability that the estimate is less than zero (Fig. 3A, right panel).
There was no evidence that the treatment effects became more important over time because there was no directional trend in the random year effects (Fig. A2-2).

@@

The results of our five year experiment in a sagebrush steppe conform to two of our four predictions, depending on treatment.
Under chronic drought, neither ecosystem functional response nor community composition changed (Fig. 1, top left).
But under irrigation, ecosystem functional response was different from the control treatment while community composition remained unchanged (Fig. 1, top right).
Thus, we found some evidence for a saturating response at high water availability (Fig. 3), but the response of ANPP to soil moisture was weak overall (Table 1).
<!---
The results of our five year experiment in a sagebrush steppe conform to the first of our four predictions: neither ecosystem functional response nor community composition changed with chronic alteration in water availability (Fig. 1, top left).
--->

The similarity of ecosystem functional response (Fig. 3) and community composition (Fig. 5) between drought and control treatments is surprising because grasslands generally, and sagebrush steppe specifically, are considered water-limited systems.
Indeed, we expected ecosystem functional response, community composition, or both to change under the drought treatment, landing us in any box of Fig. 1 \emph{except} the top left.
So, why did our dourhgt treatment fail to induce ecosystem or community responses?
We can think of three reasons; two are limitations of our study, and one is the life history traits of the species in our focal communities.
We first discuss the potential limitations of our study, and then discuss the biological explanation.

>>>>

Cumulative March-June soil moisture had a weak positive effect on ANPP (Table 1; Fig. 3), but the effect is associated with high uncertainty, with credible intervals that overlap zero, regardless of treatment (Table 1).
Ecosystem functional response was similar among treatments (Table 1; Fig. 3), but there is evidence that the slope for the irrigation treatment is less than the slope for the control treatment.
This evidence comes from interpreting the posterior distribution of the slope offset for the irrigation treatment, from which we calculate a 98% probability that the estimate is less than zero (Fig. 3A, right panel).
There was no evidence that the treatment effects became more important over time because there was no directional trend in the random year effects (Fig. A2-2).

@@

The results of our five year experiment in a sagebrush steppe conform to two of our four predictions, depending on treatment.
Under chronic drought, neither ecosystem functional response nor community composition changed (Fig. 1, top left).
But under irrigation, ecosystem functional response was different from the control treatment while community composition remained unchanged (Fig. 1, top right).
Thus, we found some evidence for a saturating response at high water availability (Fig. 3), but the response of ANPP to soil moisture was weak overall, regardless of treatment (Table 1).
<!---
The results of our five year experiment in a sagebrush steppe conform to the first of our four predictions: neither ecosystem functional response nor community composition changed with chronic alteration in water availability (Fig. 1, top left).
--->

The similarity of ecosystem functional response (Fig. 3) and community composition (Fig. 5) between drought and control treatments is surprising because grasslands generally, and sagebrush steppe specifically, are considered water-limited systems.
Indeed, we expected ecosystem functional response, community composition, or both to change under the drought treatment, landing us in any box of Fig. 1 \emph{except} the top left.
So, why did our drought treatment fail to induce ecosystem or community responses?
We can think of three reasons; two are limitations of our study, and one is the life history traits of the species in our focal communities.
We first discuss the potential limitations of our study, and then discuss the biological explanation.
